---
title: 'Financial Compensation between Federal States in Germany'
author: 'Workshop: Advanced R Programming'
date: 'Report Created: `r Sys.time()`'
output:
  html_document:
    toc: yes
    toc_float: yes
    code_folding: hide
    code_download: true
    theme: default
params:
  year1:
    label: "First (earlier) year for arrow chart comparison?"
    value: 1975
    min: 1950
    max: 2018
    step: 1
  year2:
    label: "Second (later) year for arrow chart comparison?"
    value: 2015
    min: 1950
    max: 2018
    step: 1
  state:
    label: "Pick a Federal State for line chart"
    value: "Niedersachsen"
    input: select
    choices: !r levels(laenderfinanz$Bundesland)
---

```{r param_year_plausib}

# Test, ob year1 vor year2 liegt:

if (params$year2 <= params$year1) {
  stop("Second year must be later than first year!\nPlease knit again with different choices for years.")
}

```


```{r setup, include=FALSE}

library(tidyverse)
library(glue)
library(plotly)

knitr::opts_chunk$set(echo = TRUE)
# knitr::opts_chunk$set(comment = NA)

laenderfinanz <- readRDS("Laenderfinanzausgleich.rds")
```


# Data

The following analyses are based on a dataset of `r nrow(laenderfinanz)` rows and `r ncol(laenderfinanz)` columns.


# Some Visualizations

## Arrow Chart, 2018 vs. 1995

1995 vs. 2018 is an interesting comparison:

* In 1995, the East German federal states were included for the first time.
* 2018 is the most recent time in this dataset.
* There were massive shifts in same states.

```{r arrows, echo = TRUE}

df <- laenderfinanz %>%
  select(-Typ) %>%
  pivot_wider(names_from = Jahr, values_from = Finanzausgleich)

ggplot(df, aes(x = `1995`, xend = `2018`,
               y = reorder(Bundesland, `2018`), yend = reorder(Bundesland, `2018`))) +
  geom_segment(size = 1.5, arrow = arrow(length = unit(0.3, "cm"))) +
  labs(x = "Financial Compensation, unit = 1 Million Euro",
       y = NULL,
       title = "Financial Compensation between Federal States\n1995 vs. 2018",
       caption = "Data: https://de.wikipedia.org/wiki/L채nderfinanzausgleich#Finanzvolumen") +
  theme_bw() +
  theme(text = element_text(size = 12))


```

## One Federal State: Select via Parameter

You chose to select `r params$state`.

```{r state}

chart <- laenderfinanz %>% 
  filter(Bundesland == params$state) %>% 
  ggplot(aes(x = Jahr, y = Finanzausgleich)) +
  geom_line(col = "blue") +
  theme_bw() +
  labs(title = glue("Financial compensation: {params$state}"),
       x = "Year", y = "Compensation", caption = "Data: https://de.wikipedia.org/wiki/L채nderfinanzausgleich#Finanzvolumen")

ggplotly(chart)

```


## Tidy Eval: Arrow Chart, `r params$year2` vs. `r params$year1`

Greift auf Parameter zur체ck ...

```{r arrows_params}

year1c <- as.name(params$year1)
year2c <- as.name(params$year2)

df <- laenderfinanz %>%
  select(-Typ) %>%
  pivot_wider(names_from = Jahr, values_from = Finanzausgleich) %>% 
  select(Bundesland, {{year1c}}, {{year2c}}) %>% 
  na.omit()

ggplot(df, aes(x = {{year1c}}, xend = {{year2c}},
               y = reorder(Bundesland, {{year2c}}),
               yend = reorder(Bundesland, {{year2c}}))) +
  geom_segment(size = 1.5, arrow = arrow(length = unit(0.3, "cm"))) +
  labs(x = "Financial Compensation, unit = 1 Million Euro",
       y = NULL,
       title = glue("Financial Compensation between Federal States\n{params$year1} vs. {params$year2}"),
       caption = "Data: https://de.wikipedia.org/wiki/L채nderfinanzausgleich#Finanzvolumen") +
  theme_bw() +
  theme(text = element_text(size = 12))
```

